Hybrid platforms and bargaining

### 2023-04-20 src/presentation/topics_talk.qmd
Add manim figure for results and appendix

@@

>>>>

::: {.fragment fragment-index=1}
  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
:::
::: {.fragment fragment-index=1}
  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
:::
::: {.fragment fragment-index=1}
  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
:::
::: {.fragment fragment-index=1}
  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
:::
::: {.fragment fragment-index=1}
  <video height="500" data-autoplay src="../../out/manim_figures/videos/equilibrium_outcomes/800p60/sections/draw_graph.mp4" />
:::

@@

# Appendix

## Baseline model

:::: {.columns}

::: {.column width="100%"}

Set of all players: $N = \{P, A_1, \dots, A_n\}$

**Assumption**: the platform is the only way for firms to
reach users and that all $n$ firms are identical
$$
v(C) = \begin{cases}
   0                                           & \text{if } P \notin C \\
   f\left(\frac{|C \setminus \{P\}|}{n}\right) & \text{otherwise}.
\end{cases}
$$
$\forall\, C \subset N$.
:::

::: {.notes}
 - Not only platforms. Also describes
   - upstream-downstream setups
   - generally any setting with an important large players and many identical small ones
:::

## Value of the platform

:::: {.columns}

::: {.column width="40%"}

Characteristic function:
$$
\scriptsize
v(C) = \begin{cases}
   0 \;\text{ if } P \notin C \\
   f\left(\frac{|C \setminus \{P\}|}{n}\right)
\end{cases}
$$

::: {.fragment .fade-in fragment-index=2}
Shapley value:
$$
\scriptsize
\varphi_P^n(f) = \frac{1}{n+1} \sum_{k=0}^{n} f(k)
$$
:::
::: {.fragment .fade-in fragment-index=5}
$$
\scriptsize
\to \int_0^1 f(t) \, \mathrm{d}t
$$
:::

::: {.column width="60%"}

::: {.fragment fragment-index=1}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/draw_bars.mp4" />
:::
::: {.fragment fragment-index=2}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/a_nof.mp4" />
:::
::: {.fragment fragment-index=3}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/a_bench.mp4" />
:::
::: {.fragment fragment-index=4}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/a_barg.mp4" />
:::
::: {.fragment fragment-index=6}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/pi_p_all.mp4" />
:::

::: {.notes}
 - Think of the previous figure with the orderings
 - Main insight: each ordering with the platform at position $k$ has the same probability
:::
